Optimization of String Rewriting Operations for 3D Fractal Generation with Genetic Algorithms

### 2018-07-11 Optimization-of-String-Rewriting-Operations-for-3D-Fractal-Generation-with-Genetic-Algorithms/paper.tex
References were extended.

The extension of the idea for fractal generation from 2D to 3D space shows that in 3D space the process is much more time consuming than in the 2D space. Voxel based representation of 3D objects consumes too much computational resources. Generated objects are not applicable in real use, but results achieved are promising for further research of the fractal nature of the world in which all we are living.

@@

\bibitem{nettleton01} Nettleton D.J., Garigliano R., \textit{Evolutionary algorithms and a fractal inverse problem}, Biosystems, vol. 33, issue 3, ISSN 0303-2647, 221--231, 1994.

@@

\bibitem{balabanov01} Balabanov, T., \textit{The idea of Jack Hodkinson for fractal generation implemented in 3D version}, http://github.com/TodorBalabanov/Jack-Hodkinson-3D-Fractal , 2018.

>>>>

The extension of the idea for fractal generation from 2D to 3D space shows that in 3D space the process is much more time consuming than in the 2D space. Some speed-ups are possible by parallel implementation of the genetic algorithm \cite{shonkwiler02}. Voxel based representation of 3D objects consumes a lot of computational resources and generated objects are with limited usefulness. A possible application is compression of 3D images, which is similar to the idea of 2D images compression \cite{vences01,albundi01}. Achieved results are promising for further research of the fractal nature of the world in which all we are living.

@@

\bibitem{nettleton01} Nettleton D.J., Garigliano R., \textit{Evolutionary algorithms and a fractal inverse problem}, Biosystems, vol. 33, no. 3, ISSN 0303-2647, 221--231, 1994.

@@

\bibitem{balabanov01} Balabanov T., \textit{The idea of Jack Hodkinson for fractal generation implemented in 3D version}, http://github.com/TodorBalabanov/Jack-Hodkinson-3D-Fractal , 2018.

\bibitem{shonkwiler02} Shonkwiler R., \textit{Parallel Genetic Algorithms}, Proceedings of the Fifth International Conference on Genetic Algorithms, Morgan Kaufmann, CA, 199--205, 1993.

\bibitem{vences01} Vences L., Rudomin I., Carretera K., Guadalupe L., \textit{Genetic Algorithms for Fractal Image and Image Sequence Compression},  
Proceedings of Comptacion Visual, 35--44, 1997.

\bibitem{albundi01} Al-Bundi S.S., Al-Saidi N.M., Al-Jawari N.J., \textit{Crowding Optimization Method to Improve Fractal Image Compressions Based Iterated Function Systems}, International Journal of Advanced Computer Science and Applications, vol. 7, no. 7, 392--401, 2016.
